---
title: "Tutorial of sraster"
author: "DGT Portugal, William Martinez"
date: "05/08/2019"
fig_caption: TRUE
output:
  html_document: 
    theme: journal
    toc: true
    toc_depth: 4
    number_section: true
    code_folding: hide
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
#library(kableExtra)
```


# classification

```{r}
source('\\\\dgt-699\\IPSTERS\\sraster\\R\\clip_raster.R')

set.seed(123)
file_directory = 'C:\\IPSTERS\\sraster\\ins5\\sampling_6\\majority_rule_classification_pca'
list_files = lapply(list.files(file_directory),function(x){paste0(file_directory,"\\",x)})

group_by = 'Object'
nsamples = 7000

data_random_split = lapply(list_files, sampling_strata, nsamples, group_by)

#===============================
#classification random forest
#===============================

data_random_split2 = lapply(data_random_split, function_train_selection)

data_random = do.call("rbind",data_random_split2)
#write.csv(data_random,"output5.csv")

#===============================
#Removing nans
#===============================

data_random2 = remove_na_df(data_random)
#removing columns with categorical levels
train = data_random2[,-c(1,2,3,4,189)]

#===============================
#Modelling
#===============================
set.seed(444)
model_rf = randomForest::randomForest(Label~. , data = train,ntree = 500)
print(model_rf)
randomForest::importance(model_rf)
```


# Prediction

```{r, message=FALSE, warning=FALSE}

#===============================
#Example
#===============================

library(rgdal)
library(sf)
library(rasterVis)
library(stars)
library(raster)

file_shape = '\\\\dgt-699\\IPSTERS\\COS2015\\Tiles_prediction.shp'
tile = st_read(file_shape)
```


# Example Polygon

```{r, message=FALSE, warning=FALSE}
sub_tile_analysis =  tile[which(tile$Prediction == 'Tile_111'),]
shape = sub_tile_analysis[1,]
```

## Images ST

```{r, message=FALSE, warning=FALSE}
images_folder = '\\\\dsgig-12\\dsgig-12-intenso\\Theia_S2process\\T29SND\\composites'
name_files = list.files(images_folder, pattern = "\\.tif$")
paths_images = paste0(images_folder, '//', name_files)
paths_images = paths_images[1:12]
```



## sraster object

For the 92266 polygon we want to extract the spectral and temporal information associated to Snetinel 2 2018. The function as_raster also provides NDVI index. Since we have 9 images with 10 bands of sentinel 2, plus NDVI per image, in total we have 99 layers for our cluster analysis.

```{r }
names_bands = c('Band_1','Band_2', 'Band_3', 'Band_4', 'Band_5', 'Band_6','Band_7','Band_8', 'Band_9','Band_10')
name_times = c('ST_Oct_2017','ST_Nov_2017','ST_Dec_2017','ST_Jan_2018','ST_Feb_2018','ST_Mar_2018','ST_Apr_2018','ST_May_2018','ST_Jun_2018','ST_Jul_2018','ST_Aug_2018','ST_Sep_2018')
result = as_sraster(shape,paths_images,names_bands, name_times)

plot(funct_plot((result$data[["ST_Oct_2017"]][,,1])))
#st_write(as.data.frame(result),"output_11.csv",layer_options = "GEOMETRY=AS_XY")
```
## Adding NDVI and converting to sraster object

```{r }
images_folder_ndvi = '\\\\dsgig-12\\dsgig-12-intenso\\Theia_S2process\\T29SND\\composites\\indices'
name_files_ndvi = list.files(images_folder_ndvi, pattern = "\\NDVI.tif$")
paths_images_ndvi = paste0(images_folder_ndvi, '//', name_files_ndvi)
#converting the info in sraster object
result_ndvi = as_sraster(shape,paths_images_ndvi,names_bands = c("NDVI"),name_times)
plot(funct_plot((result_ndvi$data[["ST_Oct_2017"]][,,1])))
```


## Adding NDBI and converting to sraster object

```{r }
images_folder_NDBI = '\\\\dsgig-12\\dsgig-12-intenso\\Theia_S2process\\T29SND\\composites\\indices'
name_files_NDBI = list.files(images_folder_NDBI, pattern = "\\NDBI.tif$")
paths_images_NDBI = paste0(images_folder_NDBI, '//', name_files_NDBI)
#converting the info in sraster object
result_NDBI = as_sraster(shape,paths_images_NDBI,names_bands = c("NDBI"),name_times)
plot(funct_plot((result_NDBI$data[["ST_Oct_2017"]][,,1])))
```


## Adding NDMIR and converting to sraster object


```{r }
images_folder_NDMIR = '\\\\dsgig-12\\dsgig-12-intenso\\Theia_S2process\\T29SND\\composites\\indices'
name_files_NDMIR = list.files(images_folder_NDMIR, pattern = "\\NDMIR.tif$")
paths_images_NDMIR = paste0(images_folder_NDMIR, '//', name_files_NDMIR)
#converting the info in sraster object
result_NDMIR = as_sraster(shape,paths_images_NDMIR,names_bands = c("NDMIR"),name_times)
plot(funct_plot((result_NDMIR$data[["ST_Oct_2017"]][,,1])))
```

## stacking layers

```{r }
result_stack = stack(list(result,result_ndvi,result_NDBI, result_NDMIR))
result_stack$bands
#st_write(as.data.frame(result_stack),"output_stack.csv",layer_options = "GEOMETRY=AS_XY")
```


## Converting to a dataframe

```{r }
dfraster = as.data.frame(result_stack)
dim(dfraster)
```


## Adding stat

```{r }
dfraster_stat = add_stat(dfraster)
#st_write(as.data.frame(dfraster_stat),"output_tt12.csv",layer_options = "GEOMETRY=AS_XY")
```

## Prediction

```{r }
library(caret)
st_data = dfraster_stat[,-1]
st_geometry(st_data) = NULL
pred_st_data = predict(model_rf, st_data)
dfraster_stat$Prediction = pred_st_data
#st_write(as.data.frame(dfraster_stat),"output_prediction.csv",layer_options = "GEOMETRY=AS_XY")
```


```{r }
library(raster)
# create spatial points data frame
spg <- data.frame(sf::st_coordinates(dfraster_stat),value=pred_st_data)
coordinates(spg) <- ~ X + Y
# coerce to SpatialPixelsDataFrame
gridded(spg) <- TRUE
# coerce to raster
rasterDF <- raster(spg)
plot(rasterDF)
```

# workflow

```{r }
library(raster)
for(k in unique(tile$Prediction)){
    index_stile = which(tile$Prediction == k)
    sub_tile = tile[index_stile,]
    list_raster = list()
    for(i in unique(sub_tile$OBJECTI)){
          shape = sub_tile[which(sub_tile$OBJECTI == i),]
          result = as_sraster(shape,paths_images,names_bands, name_times)
          result_ndvi = as_sraster(shape,paths_images_ndvi,names_bands = c("NDVI"),name_times)
          result_NDBI = as_sraster(shape,paths_images_NDBI,names_bands = c("NDBI"),name_times)
          result_NDMIR = as_sraster(shape,paths_images_NDMIR,names_bands = c("NDMIR"),name_times)
          result_stack = stack(list(result,result_ndvi,result_NDBI, result_NDMIR))
          dfraster = as.data.frame(result_stack)
          dfraster_stat = add_stat(dfraster)
          st_data = dfraster_stat[,-1]
          st_geometry(st_data) = NULL
          pred_st_data = predict(model_rf, st_data)
          #raster
          spg <- data.frame(sf::st_coordinates(dfraster_stat),value=pred_st_data)
          coordinates(spg) <- ~ X + Y
          # coerce to SpatialPixelsDataFrame
          gridded(spg) <- TRUE
          # coerce to raster
          list_raster[[i]] <- raster(spg)
          cat('Done squere ', i, " of tile ", k)
          }
    list_raster$fun <- max
    list_raster= list_raster[which(!sapply(list_raster, is.null))]
    raster_f <- do.call(mosaic, list_raster)
    raster::crs(raster_f) <- raster::crs(raster(paths_images[1]))
    file_tif = paste0('\\\\dgt-699\\IPSTERS\\COS2015\\Map\\',k,'.tif')
    raster::writeRaster(raster_f,file_tif)
    cat('done tile ', k)
}
```

# mosaic

```{r }
#list_raster$fun <- max
#raster_f <- do.call(mosaic, list_raster)
#raster::crs(dfraster_stat)
#raster::writeRaster(raster_f,"testingf.tif")
```
