---
title: "Tutorial of sraster: working with HRL"
author: "DGT Portugal, William Martinez"
date: "05/08/2019"
fig_caption: TRUE
output:
  html_document: 
    theme: journal
    toc: true
    toc_depth: 4
    number_section: true
    code_folding: hide
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
#library(kableExtra)
```

# Introduction

The attempt of this tutorial is to document the implmentation of the cluster analysis developed in Pari's paper. 


```{r, message=FALSE, warning=FALSE}
source('C:\\IPSTERS\\sraster\\R\\clip_raster.R')

library(rgdal)
library(sf)
library(rasterVis)
library(stars)
library(raster)

file_shape = 'C:\\IPSTERS\\COS2015\\COS2015_v2_08_02_2019_clip.shp'
legend = st_read(file_shape)
table(legend$Legend)

class_analysis = 'broadleaf'

legend_class = legend[which(legend$Legend == class_analysis),]
rm(legend)
```

## Query Polygons based on HRL

To transform all HRL mask to polygon vector may represent a really demanding computationall task. This task is mean to later on applying an intersection wiht the polygons of COS. However, before that intersection we require that the mask layer shrinks boundaries in 20 meters in order to have higher certainty that the pixel is covering this kind of class. 

### raster to points

```{r}
file_mask = c('C:\\IPSTERS\\sraster\\images\\Mask_broadleaf.tif')
hrl = raster(file_mask)
hrl_points = st_as_sf(rasterToPoints(hrl,spatial = TRUE))
```


### Intersection
```{r}
intersect_poly_hrl_cos = st_intersects(legend_class , hrl_points)
```


```{r}
number_points = function(x, threshold){
    if(length(x)>= threshold){
      return(length(x))
    }else
    {
      return(99999)
    }
}
#threshold: at least one pixel is intersected
len_vector = lapply(intersect_poly_hrl_cos, number_points, threshold = 20)
index_poly = which(unlist(len_vector) != 99999)
legend_class_q0 = legend_class[index_poly,]
#hrl_points = NULL
```


## Size of the polygons


```{r}
library(units)
areas_poly = st_area(legend_class_q0)
boxplot(areas_poly,col = "bisque")

quantile(areas_poly,probs=c(0.25,0.5,0.65,0.75,1))
lim_max = quantile(areas_poly,probs=c(0.65))
lim_min = 10000   # Minimun mapping unit
units(lim_min) <- as_units("m^2")

areas_poly_limit = areas_poly[areas_poly >= lim_min & areas_poly < lim_max]

boxplot(areas_poly_limit,col = "bisque")

cat("Number of polygons: ", length(areas_poly_limit))
```

## Query based on area

```{r}
legend_class_q1 = legend_class_q0[which(areas_poly >= lim_min & areas_poly < lim_max),]
```


## Images

```{r, message=FALSE, warning=FALSE}
images_folder = 'C:\\IPSTERS\\IMAGES'
join_path = function(x,path_folder){
  a = strsplit(x,'[.]')
  format_file = a[[1]][length(a[[1]])]
  if(format_file == 'tif'){
    return(paste0(path_folder,'/',x))
  }
}

list_images = c("S2A_L2A_20171002-113001_T29SND.tif",
                 "S2A_L2A_20171221-112810_T29SND.tif",
                 "S2A_L2A_20180321-112321_T29SND.tif",
                 "S2A_L2A_20180619-112602_T29SND.tif",
                 "S2A_L2A_20180729-112845_T29SND.tif",
                 "S2A_L2A_20180818-112627_T29SND.tif",
                 "S2A_L2A_20180927-112959_T29SND.tif")

paths_images = unlist(lapply(list_images,join_path,images_folder))
```


## Example

We consider two shapes, one polygon corresponds to the original one extracted from COS 2015 and the another one after boundary extraction of 20m around original polygon.

```{r }
shape = legend_class_q1[1,]
plot(st_geometry(shape),border='red')
```

```{r }
names_bands = c('B2','B3', 'B4', 'B5', 'B6', 'B7','B8','B8A', 'B11','B12')
result = as_sraster(shape,paths_images,names_bands)
plot(funct_plot((result$data[["2017-10-02"]][,,1])))
```
## Adding NDVI and converting to sraster object

```{r }
list_images_ndvi = c("S2A_L2A_20171002-113001_T29SND_NDVI.tif",
                 "S2A_L2A_20171221-112810_T29SND_NDVI.tif",
                 "S2A_L2A_20180321-112321_T29SND_NDVI.tif",
                 "S2A_L2A_20180619-112602_T29SND_NDVI.tif",
                 "S2A_L2A_20180729-112845_T29SND_NDVI.tif",
                 "S2A_L2A_20180818-112627_T29SND_NDVI.tif",
                 "S2A_L2A_20180927-112959_T29SND_NDVI.tif")

paths_images_ndvi = unlist(lapply(list_images_ndvi,join_path,images_folder))

result_ndvi = as_sraster(shape, paths_images_ndvi, names_bands = c("NDVI"))
plot(funct_plot((result_ndvi$data[["2017-10-02"]][,,1])))
#st_write(as.data.frame(result_ndvi),"output_ndvi.csv",layer_options = "GEOMETRY=AS_XY")
```


## Adding NDBI and converting to sraster object

```{r }
list_images_NDBI = c("S2A_L2A_20171002-113001_T29SND_NDBI.tif",
                 "S2A_L2A_20171221-112810_T29SND_NDBI.tif",
                 "S2A_L2A_20180321-112321_T29SND_NDBI.tif",
                 "S2A_L2A_20180619-112602_T29SND_NDBI.tif",
                 "S2A_L2A_20180729-112845_T29SND_NDBI.tif",
                 "S2A_L2A_20180818-112627_T29SND_NDBI.tif",
                 "S2A_L2A_20180927-112959_T29SND_NDBI.tif")

paths_images_NDBI = unlist(lapply(list_images_NDBI,join_path,images_folder))

result_NDBI = as_sraster(shape, paths_images_NDBI, names_bands = c("NDBI"))
plot(funct_plot((result_NDBI$data[["2017-10-02"]][,,1])))
result_NDBI
#st_write(as.data.frame(result_NDBI),"output_ndbi.csv",layer_options = "GEOMETRY=AS_XY")
```


## Adding NDMIR and converting to sraster object


```{r }
list_images_NDMIR = c("S2A_L2A_20171002-113001_T29SND_NDMIR.tif",
                 "S2A_L2A_20171221-112810_T29SND_NDMIR.tif",
                 "S2A_L2A_20180321-112321_T29SND_NDMIR.tif",
                 "S2A_L2A_20180619-112602_T29SND_NDMIR.tif",
                 "S2A_L2A_20180729-112845_T29SND_NDMIR.tif",
                 "S2A_L2A_20180818-112627_T29SND_NDMIR.tif",
                 "S2A_L2A_20180927-112959_T29SND_NDMIR.tif")

paths_images_NDMIR = unlist(lapply(list_images_NDMIR,join_path,images_folder))

result_NDMIR = as_sraster(shape, paths_images_NDMIR, names_bands = c("NDMIR"))
plot(funct_plot((result_NDMIR$data[["2017-10-02"]][,,1])))
result_NDMIR
#st_write(as.data.frame(result_NDMIR),"output_NDMIR.csv",layer_options = "GEOMETRY=AS_XY")
```

## stacking layers

```{r }
result_stack = stack(list(result, result_ndvi,result_NDBI, result_NDMIR))
result_stack$bands
#st_write(as.data.frame(result_stack),"output_stack.csv",layer_options = "GEOMETRY=AS_XY")
```


### Coniferos Mask HRL

```{r }
mask_hrl_sraster = as_sraster(shape, file_mask, names_bands = c("mask"))
mask_hrl  = mask_hrl_sraster$data[[1]][,,1]
plot(funct_plot((mask_hrl)))
```

### Extracting spectral temporal information using HRL boundaries

```{r }
result_clip = clip_sraster(result_stack, mask = mask_hrl, type = "No rule")
plot(funct_plot((result_clip$data[["2017-10-02"]][,,11])))
```

## K means

Internally the number of cluster is defined by the Calinski-Harabasz index. As result, we have n clusters

```{r }
cluster_matrix = kmeans_sraster(result_clip)

mask_raster = funct_plot(cluster_matrix)
mask_raster = as.factor(mask_raster)
rat <- levels(mask_raster)[[1]]
name_clusters = names(table(cluster_matrix))
rat[["cluster"]] <- name_clusters
levels(mask_raster) <- rat

levelplot(mask_raster,col.regions=c("red","blue","yellow","green","black","orange"))
```


### Extracting spectral temporal information with Majority rule

```{r }
result_clip_cluster = clip_sraster(result_clip, mask = cluster_matrix, type ="Majority rule")
plot(funct_plot((result_clip_cluster$data[["2017-10-02"]][,,11])))
#st_write(as.data.frame(result_clip),"output_clip.csv",layer_options = "GEOMETRY=AS_XY")
```

# Working with more polygons

Well, this workflow also attempts to construct a database with the spectral-temporal information that must be part of the trainig and validation modelling. So here we want to evaluate haw fast we can retrieve pseudotraining and put it a file that later on we will use for modelling. 

```{r }
n_samples = 40
set.seed(123)   #setting same random selection for testing
index = sample(1:dim(legend_class_q1)[1], n_samples,replace = FALSE)
```


The following script contains the workflow that generalize the process done with the polygon of water done above. We require 3.5 seconds per polygon, so working with 20 this process can take one minute and 10 seconds more.

```{r}
workflow <- function(shape, paths_images, type){
          result = as_sraster(shape,paths_images,names_bands=c("B2","B3","B4","B5","B6","B7","B8","B8A","B11","B12"))
          result_ndvi = as_sraster(shape, paths_images_ndvi, names_bands = c("NDVI"))
          result_NDBI = as_sraster(shape, paths_images_NDBI, names_bands = c("NDBI"))
          result_NDMIR = as_sraster(shape, paths_images_NDMIR, names_bands = c("NDMIR"))
          result_stack = stack(list(result, result_ndvi,result_NDBI, result_NDMIR))
          #mask HRL
          mask_hrl_sraster = as_sraster(shape, file_mask, names_bands = c("mask"))
          mask_hrl  = mask_hrl_sraster$data[[1]][,,1]
          
          #checking if the intersection has information, otherwise return NULL
          if(all(is.na( mask_hrl))){
             return(NULL)
          }
          else if(length( which(!is.na(mask_hrl))) < 20){
             return(NULL)
          }
          else{
            result_clip = clip_sraster(result_stack, mask = mask_hrl, type = "No rule")
            #mask cluster
            cluster_matrix = kmeans_sraster(result_clip)
            if(all(is.na(cluster_matrix))){
              return(NULL)
            }
            else{
              result_clip_cluster = clip_sraster(result_clip, mask = cluster_matrix, type)
              return(as.data.frame(result_clip_cluster))            
            }
          }
}
```


## Cluster analysis


```{r }
#query 2  eval= FALSE 
legend_class_q2 = legend_class_q1[index,]

list_shapes = split(legend_class_q2,legend_class_q2$OBJECTI)

result_list_majrule = lapply(list_shapes, workflow, paths_images, type ="Majority rule")

result_df_majrule = do.call("rbind",result_list_majrule)
```


## Plot signal

```{r }
library(reshape2)
library(ggplot2)
index_indvi = grep("NDVI",colnames(result_df_majrule))

result_df_majrule_ndvi = result_df_majrule[,c(1,index_indvi)]

st_geometry(result_df_majrule_ndvi) = NULL

result_aggregate_time = aggregate(result_df_majrule_ndvi, by = list(result_df_majrule_ndvi$Object), FUN = median, na.rm =TRUE)
resultmelt <- melt(result_aggregate_time[,-1], id.vars = "Object")
#removing ndvi text
resultmelt$variable <- as.Date(substr(resultmelt[,c("variable")], 1, 10))
resultmelt$Object <- as.factor(resultmelt$Object)

#ggplot
p1 <- ggplot(resultmelt, aes(variable, value, group = Object)) + 
  geom_line(color="red") + theme(legend.position="top")
print(p1)
```


## Bhattacharyya distance

```{r }
y = result_df_majrule[,c(1,index_indvi)]
st_geometry(y) <- NULL
index_preserve = b_distance(y, prob= 0.80)
result_df_majrule2 = result_df_majrule[result_df_majrule$Object %in% index_preserve, ]

#graphic 2
resultmelt$Type = "Outlier"
resultmelt[resultmelt$Object %in% index_preserve,c("Type")] = "Data"

#ggplot
p1 <- ggplot(resultmelt, aes(variable, value, group = Object)) + 
  geom_line(aes(color=Type)) + theme(legend.position="top") +
  scale_linetype_manual(values=c("twodash", "dotted"))+
  scale_size_manual(values=c(4, 4))
  
print(p1)

```



To save the results

```{r }
#eval= FALSE
st_crs(result_df_majrule)<-st_crs(legend_class)
st_crs(result_df_majrule2)<-st_crs(legend_class)
st_write(result_df_majrule, paste0("output_",class_analysis,"_majrule.csv"), layer_options = "GEOMETRY=AS_XY")
st_write(result_df_majrule2, paste0("output_",class_analysis,"_majrule_bdist.csv"), layer_options = "GEOMETRY=AS_XY")
#st_write(result_df_ndvirule2, paste0("output_",class_analysis,"_ndvirule.csv"), layer_options = "GEOMETRY=AS_XY")
```


#saving pixel values without processing


```{r }

workflow2 <- function(shape, paths_images, type){
          result = as_sraster(shape,paths_images,names_bands=c("B2","B3","B4","B5","B6","B7","B8","B8A","B11","B12"))
          result_ndvi = as_sraster(shape, paths_images_ndvi, names_bands = c("NDVI"))
          result_NDBI = as_sraster(shape, paths_images_NDBI, names_bands = c("NDBI"))
          result_NDMIR = as_sraster(shape, paths_images_NDMIR, names_bands = c("NDMIR"))
          result_stack = stack(list(result, result_ndvi,result_NDBI, result_NDMIR))
          return(as.data.frame(result_stack))
          }
```




```{r }

indeces_polygons = unique(result_df_majrule$Object)
legend_class_q3 = legend_class_q2[legend_class_q2$OBJECTI %in% indeces_polygons,]

list_shapes = split(legend_class_q3,legend_class_q3$OBJECTI)

result_list_nr = lapply(list_shapes, workflow2, paths_images, type ="No rule")
result_df_nr = do.call("rbind",result_list_nr)
st_crs(result_df_nr)<-st_crs(legend_class)
st_write(result_df_nr, paste0("output_",class_analysis,"_norule.csv"), layer_options = "GEOMETRY=AS_XY")
```


```{r }
#rm(list=ls())
#gc()
```


